\Title

### 2020-02-18 manuscript/manuscript.tex
Start improving source distributions comparison

Compare the accuracy of the predictions made by each source distribution.
Need an objective way to compare them.
Propose a synthetic gravity model made out of prisms of different sizes and
density contrasts.
Create a regular grid of observation points where the gravitational effect of
the synthetic model will be computed.
Call it the \emph{target grid}.
Generate synthetic surveys above the same synthetic model and compute the
gravitational effect of the model on each survey.
Use each source distribution to predict values based on the ones obtained on
each survey onto the same grid points of the \emph{target grid}.
Score each interpolation by comparing the predicted values with the
\emph{target grid}.
Finally compare the accuracy of the predictions made by each source
distribution.

@@

Describe forward model made out of prisms.
Show prisms model?

>>>>

%Compare the accuracy of the predictions made by each source distribution.
%Need an objective way to compare them.
%Propose a synthetic gravity model made out of prisms of different sizes and
%density contrasts.
%Create a regular grid of observation points where the gravitational effect of
%the synthetic model will be computed.
%Call it the \emph{target grid}.
%Generate synthetic surveys above the same synthetic model and compute the
%gravitational effect of the model on each survey.
%Use each source distribution to predict values based on the ones obtained on
%each survey onto the same grid points of the \emph{target grid}.
%Score each interpolation by comparing the predicted values with the
%\emph{target grid}.
%Finally compare the accuracy of the predictions made by each source
%distribution.

Our goal is to to compare the performance of all source distributions from
Table~\ref{tab:source-distributions} when predicting harmonic field data using
the equivalent layer technique.
To do so we have created a synthetic model made out of prisms of different
shape and density contrasts.
The gravitational effect of this synthetic model have been computed on two
different set of observation points that we will call \emph{synthetic surveys}:
a ground and an airborne survey.
Its effect have also been computed on a regular grid at a constant height which
we will use as the \emph{target} values of the harmonic field.
Then the data from each synthetic survey is interpolated on the same grid
points as the \emph{target} grid using each source
distribution with different sets of parameters.
Each prediction is then scored against the \emph{target} grid and keep the one
that achieves the highest score.
We can then quantitatively compare how accurate is each source distribution at
predicting unobserved data on each synthetic survey and quantify the
computational load needed to do it.

@@

%Describe forward model made out of prisms.
%Show prisms model?

The synthetic model is made out of \textbf{number} number of prisms distributed
on a region of 100km$\times$100km between 10km deep and surface level.
